Case for Support

### 2021-11-17 application/narrativeCVRapela.tex
Added

\section{Prof.\ Maneesh Sahani -- narrative CV}

@@

Prof.\ Sahani is a Professor of Theoretical Neuroscience and Machine
Learning, and director of the Gatsby Computational Neuroscience Unit
at UCL.
%
As such, he is resident in the UK, and holds an open-ended academic
employment contract with UCL.

@@

Prof.\ Sahani has authored over 100 peer-reviewed scientific papers,
with an h-index (computed by Google scholar) of 47.

GPFA

PLDS

Grant funding?

@@

% From QQR:
\subsection{Contributions to teams and development}

As a PI, I have supervised a total of \textbf{X} students and \textbf{X} postdocs.  
In the last five years, 4 of students have moved to postdoctoral positions (at
Aalto, Cambridge, CMU and Stanford), 1 works at DeepMind, and 1 holds a faculty offer at Shanghai Tech.  In all, 8 previous students have now secured faculty (or group leader) positions at Cambridge, CMU, Columbia, Copenhagen, Janelia (2), Pittsburgh and Shanghai.
%
Of the postdoctoral fellows I have supervised in the last five years, one is doing further postdoc work in Bonn; another holds an independent
Research Fellowship at Radboud; and 2 have faculty positions: at Edinburgh and at UBC.

DARPA repair

Since 2017, I have been Director of the Gatsby Computational Neuroscience Unit, and have spearheaded its new strategic research direction. I created two new roles to support and develop the new strategy, and have recruited 2 new faculty members who have added new and highly relevant research strands to our research portfolio. As Director, I sit in the Executive Leadership Committee of the Faculty of Life Sciences at UCL.

@@

Current collaborations/networks?

I have been an active member of the academic community by contributing the development of programme content for many scientific meetings, critically assessing the intellectual content of research proposals and awards applications, and reviewing the research and strategic direction of various world-class research institutions.

I co-founded the Neural Coding, Computation and Dynamics meeting in 2007, and was in the organising committee in 2015 and 2017.

I participated in the selection committee for the Swartz Prize for Theoretical and Computational Neuroscience in 2014-2016, and was in the programme committee for the Computational and Systems Neuroscience (COSYNE) conference in 2007, becoming a  Programme Chair in 2009 and General Chair in 2010.

I was also in the Programme Committee for NIPS (now NeurIPS) in 2004 and 2006, becoming a Workshops Chair in 2008. I was also a Workshops Chair for the Computational Neuroscience Meeting from 1999 - 2003.

I was a member of the Board of Directors of the Computational Neuroscience Organization between 2003 - 2006. I am currently a member of the Society for Neuroscience and IEEE, and in 2021 became a Fellow of the European Laboratory for Learning and Intelligent Systems (ELLIS).

I currently have editorial roles in various journals including, Current Opinion in Neurobiology (Special issue on Big Data and Neuroscience), Neural Computation, Neural Systems and Circuits, Network:
Computation in Neural Systems, and Faculty of
1000, "Machine learning: life sciences" collection.

I have taken various advisory roles for international review and award panels. I reviewed the Donders Institute for Brain, Cognition and Behaviour (Netherlands), The Edmond and Lily Safra Center for Brain Sciences, Hebrew
University (Israel), and the Barcelona Summer School on Advanced Modelling of Behaviour (Spain). I have advised on awards such as the Swartz Prize for Theoretical and Computational Neuroscience (SFN, US), the Bernstein Prize (BMBF, Germany), and COSYNE.

Recently, I have acted as an advisor to a new established cross-disciplinary effort at the Indian Institute of Science in Bangalore; visiting the site a
number of times and hosting a joint workshop here at UCL.

I have sat on various grant award panels for the BMBF and DFG (Germany), and the (US) NSF/NIH collaborative research
in computational neuroscience (CRCNS) programme. I have also acted as a reviewer for proposals for the Bernstein prize, the Einstein Foundation, EPSRC, MRC, Novo Nordisk Foundation (Denmark) and NWO (Netherlands).

>>>>

\section{Dr.\ Joaquin Rapela -- narrative CV}

@@

Dr.~Joaquin Rapela is a Research Engineer Fellow at the Gatsby Computational
Neuroscience Unit (GCNU), University College London.
%
He has made a substantial contribution to the formulation and development of
the proposed project, and will be engaged with the ensuing research. He is a
Research Co-Investigator in the current application.

@@

Dr.~Rapela has acquired unique skills for the successful implementation of the
proposed project. He completed his undergraduate degree in Computer Sciences,
worked as a staff software engineer at the IBM Almaden Research Center, before
pursuing his doctoral degree in Electrical Engineer, with specialisation on
Signal Processing, at the University of Southern California.  His doctoral
dissertation, as well as his two postdoctoral positions at University of
California San Diego (UCSD) and at Brown University, focused on the use of
advances mathematical and statistical tools to characterise
electrophysiological neural signals. His
publications\footnote{https://scholar.google.com/citations?user=eXkDg2UAAAAJ\&hl=en}
demonstrate unique skills in signal processing, statistics and computational
neuroscience.

Dr.~Rapela is a strong supporter of open source software, and all his
publications are accompanied by free
code\footnote{http://www.gatsby.ucl.ac.uk/~rapela/software.htm}. While at UCSD,
he contributed to the development of EEGLAB, a large open-source project for
the characterisation of the electroencephalogram. Currently, as an Engineer
Research Fellow at the GCNU, he distributes high-quality implementations of
algorithms developed at unit (e.g., sparse variational Gaussian process factor
analysis\footnote{https://github.com/joacorapela/svGPFA}).

Another key responsibility of Dr.~Rapela at the GCNU, is to establish
collaborations with experimental neuroscientists at the SWC and help them on
the use of advanced statistical methods to process their state-of-the-art
neural recordings.

Therefore, Dr.~Rapela is excellently trained to implement all aspects
(neuroscience, statistics, signal processing, and software development) of the
proposed project.

@@

\subsection{Contributions to the development of others}

Dr.~Rapela has mentored Mr.~Tsong-Yan Lin (master student at University
California San Diego) on signal processing for processing
electroencephalographic and electrooculographic time
series~\footnote{Joaquin Rapela, Tsong-Yan Lin, Marissa Westerfield, Tzyy-Ping
Jung, and Jeanne Townsend (2012b). Assisting autistic children with wireless
EOG technology. Proceedings of the 34th Annual International Conference of the
IEEE EMBS, San Diego, California.}.

Currently, Dr.~Rapela is mentoring Ms.~Aishah Qureshi (undergraduate student at
Queens College, London), as part of the Simons Foundation Undergraduate Research
Program, on the use of linear dynamical systems to understand long-range
cortical communication in rodents.

% \subsection{Contributions to teams and development}

@@

Dr.~Rapela has reviewed articles for Vision Research, Frontiers in Neuroscience
and the Journal of Perceptual Imaging. He currently contributes to the SWC
Research Culture Working
Group~\footnote{https://sainsburywellcomecentre.github.io/RCWG/research} to
improve the research culture at the SWC and GCNU.
